---
title: "p8105_hw1_yz4719"
author: "Yuxin Zhang"
date: "2023-09-15"
output: github_document
---

```{r libraries_and_data}
library(tidyverse)
library(moderndive)
data("early_january_weather")
```

# Question 1.1: description of the dataset


This data set contains a early January weather of EWR at the year 2013 through out 15 days including variables: `r colnames(early_january_weather)`.

During this 15 days, EWR has a mean temperature of `r mean(early_january_weather$temp)`, standard deviation `r sd(early_january_weather$temp)`, a mean humid of `r mean(early_january_weather$humid)`, and a mean pressure of `r mean(early_january_weather$pressure)`.

The size of this data set is `r nrow(early_january_weather)` rows * `r ncol(early_january_weather)` columns.

The mean of the temperature is `r mean(early_january_weather$temp)` degrees.


# Question 1.2: Make a scatterplot


This scatter plot shows the relationship between time and temperature, the temperature increase as the time increase, the humidity also increase but not related close as the temperature and time does. Both humidity and temperature reached maxium around January 14th.

```{r scatterplot}
plot_temphumid = tibble(
  time_hour = early_january_weather$time_hour,
  temperature = early_january_weather$temp,
  humid = early_january_weather$humid
)

ggplot(plot_temphumid, aes(x = time_hour, y = temperature, color =  humid
)) + geom_point()

ggsave("hw1_plot_1.png")
```


# Question 2:

```{r problem_2}

sample_2 = tibble(
  samp = rnorm(10),
  vec_logical = samp > 0,
  vec_char = c("my", "name", "is", "samantha", "and", "this", "should", "be", "ten", "words"),
  vec_factor = factor(c("low", "high", "middle", "high", "middle", "middle", "low", "middle", "high", "low" ))
  )

```

## means

```{r means}
random_mean = mean(pull(sample_2, samp))
logical_mean = mean(pull(sample_2, vec_logical))
char_mean = mean(pull(sample_2, vec_char))
factor_mean = mean(pull(sample_2, vec_factor))
```

The mean function does not work on character and factor vector, but works on random sample and logical vectors.

## Convert
```{r convert_variables, eval=FALSE}
con_logical=as.numeric(pull(sample_2,vec_logical))
con_logical
con_char=as.numeric(pull(sample_2,vec_char))
con_char
con_factor=as.numeric(pull(sample_2,vec_factor))
con_factor
```

When converting these variables, the logical and factor is able to use "as.numeric" function to convert in to numeric variables, but the character variables is not able to do the same thing because it is a nominal data, and it does not have meaning. the logical variables can be convert into 0 and 1, and the factor variables can convert in to 3 different levels as 1, 2, 3.